Analysis plan

### 2023-03-22 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Updating missingness, teams for employees,  and staff rule-based groups

@@

<!-- How are you doing team classification? Are you going to generate a team -->
<!-- ID based on some rule? If so what is it, and to the prior point, how do -->
<!-- you handle changing team composition over time? -->

@@

<!-- The analysis plan is a good place to define the rules for classification -->
<!-- Re: missing supervisor name and some other values. It is possible that -->
<!-- people change supervisors or departments. Do we care about this? And how -->
<!-- should we deal with it? At a minimum, maybe we want a slightly different -->
<!-- imputation like if supervisor is the same both with earlier and later -->
<!-- nonmissing observations, use that value, otherwise use prior supervisor? -->

@@

```{r}
tbl <- 
tbl_combined %>% 
add_column(
"Treatment if missing" = c(
  "Drop observation",
  "Joined with gsa_sso from roster data, impute from other observations of same staff",
  "Impute from other observations of same staff",
  "Joined with department_id from roster data, impute from other observations of same staff",
  "Joined with full_name from roster data, drop observation",
  "Joined with supervisor_display_name from roster data, impute from other observations of same staff",
  "Label as missing",
  "Label as missing",
  "Label as missing", "Label as missing",
  "Label as missing",
  "Label as missing",
  "Drop observation",
  "Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing"
)
) %>% 
  filter(!(`Variable Name` %in% c("gsa_sso","department_id","full_name","supervisor_display_name")))
```

@@

<!-- Not sure about using percentiles for cutoffs. I would assume based on -->
<!-- classifications that more that 5 percent of teams are fully remote. For -->
<!-- individuals, i think there is more alignment on things like number of -->
<!-- days in a pay period in the office because of policy definitions for -->
<!-- people who are not remote and have to be in the office 2 days per pay -->
<!-- period. For teams maybe an extension of that basic ideas (e.g., fewer -->
<!-- than 2 days in office on average is fully remote) -->

<!-- Are all of these taking averages over the whole time period (9 months or -->
<!-- whatever)? Would we potentially want to know about things like people -->
<!-- who have more specific weekly patterns? -->

<!-- The thing that is missing here that is potentially more complicated is -->
<!-- figuring out more about how teams operate as collections of individuals. -->
<!-- For example, you could I think in this approach have a team that is 20 -->
<!-- percent average telework where everyone goes in person on Mondays and -->
<!-- the rest of the time is distributed, or you could have a team that is 20 -->
<!-- percent telework where people go in at random times and never see each -->
<!-- other. I am interested to know the extent to which people are -->
<!-- co-locating with their teams (and if some people are being left -->
<!-- out---which may help motivate some equity questions about performance -->
<!-- ratings for people who don't get face time with the boss, for example). -->
<!-- I think we are missing that level of analysis here. -->

<!-- MD: There are policy definitions of remote. 100% of days could be classified as all remote (separate rule); policy rules if you are not a full-time worker (you are a teleworker) you report two days a pay period; could align cut-offs with policy type definitions. # of days cutoff.  -->
<!-- Ben: the way I defined groups is mutually exclusive, but does not need to be that way -->
<!-- Ben: Other rules to examine -->
<!-- JB: policy side, missingness (whole groups of people missing on some dimension tells you something about data collection procedure) -->

<!-- MD: other roster data might be relevant - position category could give diff patterns for people who are analysts vs. building inspectors or supervisors vs. non supervisors, pay grade; lower pay grade less likely to have remote option -->
<!-- Ben: confusion matrix - assume that some group works in this sort of way but guess what they don’t! What is happening? -->

<!-- MD: categories: onsite flexible, onsite, remote; but not sure of levels of going in within categories. What is the average of going in? -->
<!-- MD: discretion of work patterns by regional commissioners  -->

@@

1.  **All remote** - Staff who work remotely above the 95th percentile
    <!-- could be 75th -->
2.  **Mostly remote** - Staff who work remotely between the median and
    the 95th percentile <!-- could be 75th -->
3.  **Mostly onsite** - Staff who work remotely between 5th percentile
    and the median <!-- could be 25th -->
4.  **All onsite** - Staff who work remotely below the 5th percentile
    <!-- could be 75th -->

@@

1.  **All remote** - Teams that work remotely above the 95th percentile
    <!-- could be 75th -->
2.  **Mostly remote** - Teams that work remotely between the median and
    the 95th percentile <!-- could be 75th -->
3.  **Mostly onsite** - Teams that work remotely between 5th percentile
    and the median <!-- could be 25th -->
4.  **All onsite** - Teams that work remotely below the 5th percentile
    <!-- could be 75th -->

>>>>

<!--# Done -->

@@

For staff-level analysis, the team will be defined by the employee's
supervisor. Changes in supervisors will come from staff moving teams or
an existing team changing supervisors. The size of the team will be
caluculated with the mode of staff with the supervisor over the
observations window. For employees with multiple supervisors, the size
of the team will be the average of the modes of team sizes for each
supervisor.

<!-- How are you doing team classification? Are you going to generate a team -->

<!-- ID based on some rule? If so what is it, and to the prior point, how do -->

<!-- you handle changing team composition over time? -->

<!--# Done -->

@@

<!-- The analysis plan is a good place to define the rules for classification -->

<!-- Re: missing supervisor name and some other values. It is possible that -->

<!-- people change supervisors or departments. Do we care about this? And how -->

<!-- should we deal with it? At a minimum, maybe we want a slightly different -->

<!-- imputation like if supervisor is the same both with earlier and later -->

<!-- nonmissing observations, use that value, otherwise use prior supervisor? -->

<!--# Done -->

@@

```{r}
tbl <- 
tbl_combined %>% 
add_column(
"Treatment if missing" = c(
  "Drop observation",
  "Joined with gsa_sso from roster data, impute from earlier observations of same staff",
  "Impute from earlier observations of same staff",
  "Joined with department_id from roster data, impute from earlier observations of same staff",
  "Joined with full_name from roster data, drop observation",
  "Joined with supervisor_display_name from roster data, impute from earlier observations of same staff",
  "Label as missing",
  "Label as missing",
  "Label as missing", "Label as missing",
  "Label as missing",
  "Label as missing",
  "Drop observation",
  "Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing",
"Label as missing"
)
) %>% 
  filter(!(`Variable Name` %in% c("gsa_sso","department_id","full_name","supervisor_display_name")))
```

@@

<!-- Not sure about using percentiles for cutoffs. I would assume based on -->

<!-- classifications that more that 5 percent of teams are fully remote. For -->

<!-- individuals, i think there is more alignment on things like number of -->

<!-- days in a pay period in the office because of policy definitions for -->

<!-- people who are not remote and have to be in the office 2 days per pay -->

<!-- period. For teams maybe an extension of that basic ideas (e.g., fewer -->

<!-- than 2 days in office on average is fully remote) -->

<!-- Are all of these taking averages over the whole time period (9 months or -->

<!-- whatever)? Would we potentially want to know about things like people -->

<!-- who have more specific weekly patterns? -->

<!-- The thing that is missing here that is potentially more complicated is -->

<!-- figuring out more about how teams operate as collections of individuals. -->

<!-- For example, you could I think in this approach have a team that is 20 -->

<!-- percent average telework where everyone goes in person on Mondays and -->

<!-- the rest of the time is distributed, or you could have a team that is 20 -->

<!-- percent telework where people go in at random times and never see each -->

<!-- other. I am interested to know the extent to which people are -->

<!-- co-locating with their teams (and if some people are being left -->

<!-- out---which may help motivate some equity questions about performance -->

<!-- ratings for people who don't get face time with the boss, for example). -->

<!-- I think we are missing that level of analysis here. -->

<!-- MD: There are policy definitions of remote. 100% of days could be classified as all remote (separate rule); policy rules if you are not a full-time worker (you are a teleworker) you report two days a pay period; could align cut-offs with policy type definitions. # of days cutoff.  -->

<!-- Ben: the way I defined groups is mutually exclusive, but does not need to be that way -->

<!-- Ben: Other rules to examine -->

<!-- JB: policy side, missingness (whole groups of people missing on some dimension tells you something about data collection procedure) -->

<!-- MD: other roster data might be relevant - position category could give diff patterns for people who are analysts vs. building inspectors or supervisors vs. non supervisors, pay grade; lower pay grade less likely to have remote option -->

<!-- Ben: confusion matrix - assume that some group works in this sort of way but guess what they don’t! What is happening? -->

<!-- MD: categories: onsite flexible, onsite, remote; but not sure of levels of going in within categories. What is the average of going in? -->

<!-- MD: discretion of work patterns by regional commissioners  -->

@@

1.  **All remote** - A policy definition for staff that are 100% remote.
2.  **Teleworker** - A policy definition for staff that require two days
    per pay period onsite.
3.  **Primarily remote** - Staff who work remotely above the 95th
    percentile <!-- could be 75th -->
4.  **Mostly remote** - Staff who work remotely between the median and
    the 95th percentile <!-- could be 75th -->
5.  **Mostly onsite** - Staff who work remotely between 5th percentile
    and the median <!-- could be 25th -->
6.  **Primarly onsite** - Staff who work remotely below the 5th
    percentile <!-- could be 75th -->

@@

1.  **Primarily remote** - Teams that work remotely above the 95th
    percentile <!-- could be 75th -->
2.  **Mostly remote** - Teams that work remotely between the median and
    the 95th percentile <!-- could be 75th -->
3.  **Mostly onsite** - Teams that work remotely between 5th percentile
    and the median <!-- could be 25th -->
4.  **Primarily onsite** - Teams that work remotely below the 5th
    percentile <!-- could be 75th -->
